---
title: "4. Text embeddings & document summarization"
author: "Thomas W. Jones"
date: "2/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```


# Text embeddings 
Text embeddings are particularly hot right now. While textmineR doesn't (yet) explicitly implement any embedding models like GloVe or word2vec, you can still get embeddings. Text embedding algorithms aren't conceptually different from topic models. They are, however, operating on a different matrix. Instead of reducing the dimensions of a document term matrix, text embeddings are obtained by reducing the dimensions of a term co-occurrence matrix. In principle, one can use LDA or LSA in the same way. In this case, rows of theta are embedded words. A phi_prime may be obtained to project documents or new text into the embedding space.

What follows is a quick example of this using LDA as the embedding mechanism.

```{r embedding}

# First create a TCM using skip grams, we'll use a 5-word window
# most options available on CreateDtm are also available for CreateTcm
tcm <- CreateTcm(doc_vec = movie_review$review,
                 skipgram_window = 5)

# use LDA to get embeddings into probability space
# This will take considerably longer as the TCM matrix has many more rows 
# than a DTM
embeddings <- FitLdaModel(dtm = tcm,
                          k = 100,
                          iterations = 800)

# Get an R-squared for general goodness of fit
embeddings$r2 <- CalcTopicModelR2(dtm = tcm, 
                                  phi = embeddings$phi,
                                  theta = embeddings$theta)

embeddings$r2

# Get coherence (relative to the TCM) for goodness of fit
embeddings$coherence <- CalcProbCoherence(phi = embeddings$phi,
                                          dtm = tcm)

summary(embeddings$coherence)

# Get top terms, no labels because we don't have bigrams
embeddings$top_terms <- GetTopTerms(phi = embeddings$phi,
                                    M = 5)

head(t(embeddings$top_terms))

# Create a summary table, similar to the above
embeddings$summary <- data.frame(topic = rownames(embeddings$phi),
                                 coherence = round(embeddings$coherence, 3),
                                 prevalence = colSums(embeddings$theta),
                                 top_terms = apply(embeddings$top_terms, 2, function(x){
                                   paste(x, collapse = ", ")
                                 }),
                                 stringsAsFactors = FALSE)

View(embeddings$summary[ order(embeddings$summary$prevalence, decreasing = TRUE) , ])

# Embed the documents
dtm_embed <- CreateDtm(doc_vec = movie_review$review,
                       doc_names = movie_review$id,
                       ngram_window = c(1,1))

dtm_embed <- dtm_embed[ , colnames(tcm) ] # make sure vocab lines up

embeddings$phi_prime <- CalcPhiPrime(phi = embeddings$phi,
                                     theta = embeddings$theta)

embedding_assignments <- dtm_embed / rowSums(dtm_embed)

embedding_assignments <- embedding_assignments %*% t(embeddings$phi_prime)

embedding_assignments <- as.matrix(embedding_assignments)

# get a goodness of fit relative to the DTM
embeddings$r2_dtm <- CalcTopicModelR2(dtm = dtm_embed, 
                                      phi = embeddings$phi,
                                      theta = embedding_assignments)

embeddings$r2_dtm

# get coherence relative to DTM
embeddings$coherence_dtm <- CalcProbCoherence(phi = embeddings$phi,
                                              dtm = dtm_embed)

summary(embeddings$coherence_dtm)

```

You could just as easily use LSA as your embedding, or any other dimensionality reduction/matrix factorization method. The advantge of using the `dgCMatrix` is that it is so widely supported in the R ecosystem.

Embeddings are only recently being researched. However, they may be used in very similar contexts to topic models. It's just that the "topics" are fit another way.

# Building a basic document summarizer
Let's use the above embeddings model to create a document summarizer. This will return the three most relevant sentences in each review.

```{r summaries}

library(igraph) 

# let's do this in a function

summarizer <- function(doc, phi_prime) {
  
  # recursive fanciness to handle multiple docs at once
  if (length(doc) > 1 )
    # use a try statement to catch any weirdness that may arise
    return(sapply(doc, function(d) try(summarizer(d, phi_prime))))
  
  # parse it into sentences
  sent <- stringi::stri_split_boundaries(doc, type = "sentence")[[ 1 ]]
  
  names(sent) <- seq_along(sent) # so we know index and order
  
  # embed the sentences in the model
  e <- CreateDtm(sent, ngram_window = c(1,1), verbose = FALSE)
  
  # remove any documents with 2 or fewer words
  e <- e[ rowSums(e) > 2 , ]
  
  vocab <- intersect(colnames(e), colnames(phi_prime))
  
  e <- e / rowSums(e)
  
  e <- e[ , vocab ] %*% t(phi_prime[ , vocab ])
  
  e <- as.matrix(e)
  
  # get the pairwise distances between each embedded sentence
  e_dist <- CalcHellingerDist(e)
  
  # turn into a similarity matrix
  g <- (1 - e_dist) * 100
  
  diag(g) <- 0
  
  # turn into a nearest-neighbor graph
  g <- apply(g, 1, function(x){
    x[ x < sort(x, decreasing = TRUE)[ 3 ] ] <- 0
    x
  })

  g <- pmax(g, t(g))
  
  g <- graph.adjacency(g, mode = "undirected", weighted = TRUE)
  
  # calculate eigenvector centrality
  ev <- evcent(g)
  
  # format the result
  result <- sent[ names(ev$vector)[ order(ev$vector, decreasing = TRUE)[ 1:3 ] ] ]
  
  result <- result[ order(as.numeric(names(result))) ]
  
  paste(result, collapse = " ")
}

# Let's see the summary of the first couple of reviews
docs <- movie_review$review[ 1:3 ]
names(docs) <- movie_review$id[ 1:3 ]

sums <- summarizer(docs, phi_prime = embeddings$phi_prime)

sums
```

