---
title: "5. Document summarization"
author: "Thomas W. Jones"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{5. Document summarization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", warning = FALSE
)
```

In this example we'll use text embeddings and a bit of network analysis to build a basic document summarizer. 

Many document summarizers, as the one we'll build here, do not generate language. Instead, they break a document down into sentences and then use some mechanism to score each sentence for relevance. Sentences with the top scores are returned as the "summary." For more information on summarization, a good place to start is [here](https://en.wikipedia.org/wiki/Automatic_summarization).

The summarizer we'll build is a version of the [TextRank algorithm](https://en.wikipedia.org/wiki/Automatic_summarization#Unsupervised_approach:_TextRank). We will split a document into sentences, create a nearest-neighbor network where sentences are connected to other similar sentences, and rank the sentences according to [eigenvector centrality](https://en.wikipedia.org/wiki/Eigenvector_centrality). 

We will use a word embedding model, created on a whole corpus, to project the sentences into the embedding space. Once in the embedding space, we will measure similarity between documents using [Hellinger distance](https://en.wikipedia.org/wiki/Hellinger_distance). Hellinger distance is a metric specifically for probability distributions. Since we'll use LDA to create embeddings to a probability space, it's a useful measure.

# Getting started
We'll use the movie review data set from `text2vec` again. The first thing we need to do is create a TCM and embedding model. We will skip evaluation such as R-squared, coherence, inspecting top terms, etc. However, in any real application, I'd strongly suggest evaluating your models at every step of the way. 
 

```{r embedding}
library(textmineR)

# load the data
data(movie_review, package = "text2vec")

# let's take a sample so the demo will run quickly
# note: textmineR is generally quite scaleable, depending on your system
set.seed(123)
s <- sample(1:nrow(movie_review), 500)

movie_review <- movie_review[ s , ]

# let's get those nasty "<br />" symbols out of the way
movie_review$review <- stringr::str_replace_all(movie_review$review, "<br */>", "")

# First create a TCM using skip grams, we'll use a 5-word window
# most options available on CreateDtm are also available for CreateTcm
tcm <- CreateTcm(doc_vec = movie_review$review,
                 skipgram_window = 5,
                 verbose = FALSE,
                 cpus = 2)

# use LDA to get embeddings into probability space
# This will take considerably longer as the TCM matrix has many more rows 
# than a DTM
embeddings <- FitLdaModel(dtm = tcm,
                          k = 100,
                          iterations = 200, # i recommend a larger value, 500 or more
                          cpus = 2)

# and we'll get our projection matrix
embeddings$phi_prime <- CalcPhiPrime(phi = embeddings$phi, 
                                     theta = embeddings$theta)
```

# Building a basic document summarizer
Let's use the above embeddings model to create a document summarizer. This will return the three most relevant sentences in each review.

The summarizer works best as a function, as we have many documents to summarize. The function `summarizer` is defined in the next section. However, let's look at some key bits of code in detail.

The variable `doc` represents a single document, or a single element of a character vector. 

In the code chunk below, we split the document into sentences using the `stringi` package. Then we embed each sentence under the model built on our whole corpus, above. 

```{r eval = FALSE}
  # parse it into sentences
  sent <- stringi::stri_split_boundaries(doc, type = "sentence")[[ 1 ]]
  
  names(sent) <- seq_along(sent) # so we know index and order
  
  # embed the sentences in the model
  e <- CreateDtm(sent, ngram_window = c(1,1), verbose = FALSE, cpus = 2)
  
  # remove any documents with 2 or fewer words
  e <- e[ rowSums(e) > 2 , ]
  
  vocab <- intersect(colnames(e), colnames(phi_prime))
  
  e <- e / rowSums(e)
  
  e <- e[ , vocab ] %*% t(phi_prime[ , vocab ])
  
  e <- as.matrix(e)

```

Next, we measure the distance between each of the sentences within the embedding space.

```{r eval = FALSE}
  # get the pairwise distances between each embedded sentence
  e_dist <- CalcHellingerDist(e)
```

Since we are using a distance measure whose values fall between $0$ and $1$, we can take $1 - distance$ to get a similarity. We'll also re-scale it to be between 0 and 100. (The rescaling is just a cautionary measure so that we don't run into numerical precision issues when performing calculations downstream.)

```{r eval = FALSE}
  # turn into a similarity matrix
  g <- (1 - e_dist) * 100
```

If you consider a similarity matrix to be an adjacency matrix, then you have a fully-connected graph. For the sake of potentially faster computation and with the hope of eliminating some noise, we will delete some edges. Going row-by-row, we will keep connections only to the top 3 most similar sentences.

```{r eval = FALSE}
  # we don't need sentences connected to themselves
  diag(g) <- 0
  
  # turn into a nearest-neighbor graph
  g <- apply(g, 1, function(x){
    x[ x < sort(x, decreasing = TRUE)[ 3 ] ] <- 0
    x
  })

  # by taking pointwise max, we'll make the matrix symmetric again
  g <- pmax(g, t(g))
```

Using the `igraph` package (with its own objects) to calculate eigenvector centrality. From there, we'll take the top three sentences.

```{r eval = FALSE}
  g <- graph.adjacency(g, mode = "undirected", weighted = TRUE)
  
  # calculate eigenvector centrality
  ev <- evcent(g)
  
  # format the result
  result <- sent[ names(ev$vector)[ order(ev$vector, decreasing = TRUE)[ 1:3 ] ] ]
  
  result <- result[ order(as.numeric(names(result))) ]
  
  paste(result, collapse = " ")
```

# Pulling it all together

The code below puts itall together in a single function. The first few lines vectorize the code, so that we can summarize multiple documents from a singel function call. 

```{r summaries}

library(igraph) 

# let's do this in a function

summarizer <- function(doc, phi_prime) {
  
  # recursive fanciness to handle multiple docs at once
  if (length(doc) > 1 )
    # use a try statement to catch any weirdness that may arise
    return(sapply(doc, function(d) try(summarizer(d, phi_prime))))
  
  # parse it into sentences
  sent <- stringi::stri_split_boundaries(doc, type = "sentence")[[ 1 ]]
  
  names(sent) <- seq_along(sent) # so we know index and order
  
  # embed the sentences in the model
  e <- CreateDtm(sent, ngram_window = c(1,1), verbose = FALSE)
  
  # remove any documents with 2 or fewer words
  e <- e[ rowSums(e) > 2 , ]
  
  vocab <- intersect(colnames(e), colnames(phi_prime))
  
  e <- e / rowSums(e)
  
  e <- e[ , vocab ] %*% t(phi_prime[ , vocab ])
  
  e <- as.matrix(e)
  
  # get the pairwise distances between each embedded sentence
  e_dist <- CalcHellingerDist(e)
  
  # turn into a similarity matrix
  g <- (1 - e_dist) * 100
  
  # we don't need sentences connected to themselves
  diag(g) <- 0
  
  # turn into a nearest-neighbor graph
  g <- apply(g, 1, function(x){
    x[ x < sort(x, decreasing = TRUE)[ 3 ] ] <- 0
    x
  })

  # by taking pointwise max, we'll make the matrix symmetric again
  g <- pmax(g, t(g))
  
  g <- graph.adjacency(g, mode = "undirected", weighted = TRUE)
  
  # calculate eigenvector centrality
  ev <- evcent(g)
  
  # format the result
  result <- sent[ names(ev$vector)[ order(ev$vector, decreasing = TRUE)[ 1:3 ] ] ]
  
  result <- result[ order(as.numeric(names(result))) ]
  
  paste(result, collapse = " ")
}
```

How well did we do? Let's look at summaries from the first three reviews.

```{r}
# Let's see the summary of the first couple of reviews
docs <- movie_review$review[ 1:3 ]
names(docs) <- movie_review$id[ 1:3 ]

sums <- summarizer(docs, phi_prime = embeddings$phi_prime)

sums
```

Compare that to the whole reviews yourself.

