---
title: "Introduction to textmineR"
author: "Thomas W. Jones"
date: "12/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```


## Why textmineR?

textmineR was created with three principles in mind:

1. Maximize interoperability within R's ecosystem 
2. Scaleable in terms of object storeage and computation time
3. Syntax that is idiomatic to R

R has many packages for text mining and natural language processing (NLP). The [CRAN task view on natural language processing](https://cran.r-project.org/web/views/NaturalLanguageProcessing.html) lists 53 unique packages. Some of these packages are interoperable. Some are not. 

textmineR strives for maximum interoperability in three ways. First, it uses the `dgCMatrix` class from the popular [`Matrix` package](https://cran.r-project.org/web/packages/Matrix/index.html) for document term matrices (DTMs) and term co-occurence matrices (TCMs). The `Matrix` package is an R "recommended" package with nearly 500 packages that depend, import, or suggest it. Compare that to the [`slam` package](https://cran.r-project.org/web/packages/slam/index.html) used by [`tm`](https://cran.r-project.org/web/packages/tm/index.html) and its derivatives. `slam` has an order of magnitude fewer dependents. It is simply not as well integrated. `Matrix` also has methods that make the syntax for manipulating its matrices nearly identical to base R. This greatly reduces the cognitive burden of the programmers. 

Second, textmineR relies on base R objects for corpus and metadata storage. Actually, it relies on the user to do so. textmineR's core functions `CreateDtm` and `CreateTcm` take a simple character vector as input. Users may store their corpora as character vectors, lists, or data frames. _There is no need to learn a new ['Corpus'](https://cran.r-project.org/web/packages/tm/index.html) class._

Third and last, textmineR represents the output of topic models in a consistent way, a list containing two matrices. This is described in more detail in the next section. Several topic models are supported and the simple representation means that textmineR's utility functions are useable with outputs from other packages, so long as they are represented as matrices of probabilities. (Again, see the next section for more detail.)

textmineR acheives scalability through three means. First, sparse matrices (like the `dgCMatrix`) offer significant memory savings. Second, textmineR utilizes `Rcpp` throughout for speedup. Finally, textmineR uses parallel processing by default where possible. textmineR offers a function `TmParallelApply` which implements a framework for parallel processing that is syntactically agnostic between Windows and Unix-like operating systems. `TmParallelApply` is used liberally within textmineR and is exposed for users.

textmineR does make some tradeoffs of performance for syntactic simplicity. textmineR is designed to run on a single node in a cluster computing environment. It can (and will by default) use all available cores of that node. If performance is your number one concern, see [`text2vec`](https://cran.r-project.org/web/packages/text2vec/index.html). textmineR uses some `text2vec` under the hood. 

textmineR strives for syntax that is idiomatic to R. This is, admittedly, a nebulous concept. textmineR does not create new classes where existing R classes exist. It strives for a functional programming paradigm. And it attempts to group closely-related sequential steps into single functions. This means that users will not have to make several temporary objects along the way. As an example, compare making a document term matrix in textmineR (example below) with `tm` or `text2vec`.

As a side note: textmineR's framework for NLP does not need to be exclusive to textmineR. Text mining packages in R can be interoperable with a few concepts. First, use `dgCMatrix` for DTMs and TCMs. Second, write most text mining models in a way that they can take a `dgCMatrix` as the input. Finally, keep non-base R classes to a minimum, especially for corpus and metadata management. For the most part, `text2vec` and `tidytext` adhere to these principles. 

## Corpus management

### Creating a DTM 

The basic object of analysis for most text mining applications is a document term matrix, or DTM. This is a matrix where every row represents a document and every column represents a token (word, bi-gram, stem, etc.) 

You can create a DTM with textmineR by passing a character vector. There are options for stopword removal, creation of n-grams, and other standard data cleaning. There is an option for passing a stemming or lemmatization function if you desire. (See `help(CreateDtm)` for an example using Porter's word stemmer.)

The code below uses a dataset of movie reviews included with the `text2vec` package. This dataset is used for sentiment analysis. In addition to the text of the reviews. There is a binary variable indicating positive or negative sentiment. More on this later...


```{r create_dtm}
library(textmineR)

# load movie_review dataset from text2vec
data(movie_review, package = "text2vec")

str(movie_review)

# create a document term matrix 
dtm <- CreateDtm(doc_vec = movie_review$review, # character vector of documents
                 doc_names = movie_review$id, # document names
                 ngram_window = c(1, 2), # minimum and maximum n-gram length
                 stopword_vec = c(tm::stopwords("english"), # stopwords from tm
                                  tm::stopwords("smart")), # this is the default value
                 lower = TRUE, # lowercase - this is the default value
                 remove_punctuation = TRUE, # punctuation - this is the default
                 remove_numbers = TRUE) # numbers - this is the default


dim(dtm) # 5,000 documents and 424,926 tokens


```


## Basic corpus statistics
The code below performs some basic corpus statistics. textmineR has a built in function for getting term frequencies across the corpus. This function `TermDocFreq` gives term frequencies (equivalent to `colSums(dtm)`), the number of documents in which each term appears (equivalent to `colSums(dtm > 0)`), and an inverse-document frequency (IDF) vector. The IDF vector can be used to create a TF-IDF matrix.

```{r corpus_stats_1}

# get counts of tokens across the corpus
tf_mat <- TermDocFreq(dtm = dtm)

str(tf_mat) 

# look at the most frequent tokens
head(tf_mat[ order(tf_mat$term_freq, decreasing = TRUE) , ], 10)

# look at the most frequent bigrams
tf_bigrams <- tf_mat[ stringr::str_detect(tf_mat$term, "_") , ]

head(tf_bigrams[ order(tf_bigrams$term_freq, decreasing = TRUE) , ], 10)

# it looks like we have stray html tags (<br>) that weren't stripped 
# from our documents. Let's fix that.
dtm <- dtm[ , ! stringr::str_detect(colnames(dtm),
                                    "^br$|_br$|^br_") ]

tf_mat <- TermDocFreq(dtm)

tf_bigrams <- tf_mat[ stringr::str_detect(tf_mat$term, "_") , ]

head(tf_mat[ order(tf_mat$term_freq, decreasing = TRUE) , ], 10)

head(tf_bigrams[ order(tf_bigrams$term_freq, decreasing = TRUE) , ], 10)


# summary of document lengths
doc_lengths <- rowSums(dtm)

summary(doc_lengths)
```

Often,it's useful to prune your vocabulary and remove any tokens that appear in a samall number of documents. This will greatly reduce the vocabulary size (see [Zipf's law](https://en.wikipedia.org/wiki/Zipf%27s_law)) and improve computation time. 

```{r corpus_stats_2}
# remove any tokens that were in 3 or fewer documents
dtm <- dtm[ , colSums(dtm > 0) > 3 ] # alternatively: dtm[ , tf_mat$term_freq > 3 ]

tf_mat <- tf_mat[ tf_mat$term %in% colnames(dtm) , ]

tf_bigrams <- tf_bigrams[ tf_bigrams$term %in% colnames(dtm) , ]

```

You can get a lot of mileage out of simple corpus statistics. The code below uses simple probabilistic reweighting (instead of TF-IDF) to see the unigrams and bigrams most-associated with positive and negative sentiment.

```{r corpus_stats_3}
# what words are most associated with sentiment?
tf_sentiment <- list(positive = TermDocFreq(dtm[ movie_review$sentiment == 1 , ]),
                     negative = TermDocFreq(dtm[ movie_review$sentiment == 0 , ]))

# these are basically the same, not helpful
head(tf_sentiment$positive[ order(tf_sentiment$positive$term_freq, decreasing = TRUE) , ], 10)

head(tf_sentiment$negative[ order(tf_sentiment$negative$term_freq, decreasing = TRUE) , ], 10)

# let's reweight by probability by class
p_words <- colSums(dtm) / sum(dtm) # alternatively: tf_mat$term_freq / sum(tf_mat$term_freq)

tf_sentiment$positive$conditional_prob <- 
  tf_sentiment$positive$term_freq / sum(tf_sentiment$positive$term_freq)

tf_sentiment$positive$prob_lift <- tf_sentiment$positive$conditional_prob - p_words

tf_sentiment$negative$conditional_prob <- 
  tf_sentiment$negative$term_freq / sum(tf_sentiment$negative$term_freq)

tf_sentiment$negative$prob_lift <- tf_sentiment$negative$conditional_prob - p_words

# let's look again with new weights
head(tf_sentiment$positive[ order(tf_sentiment$positive$prob_lift, decreasing = TRUE) , ], 10)

head(tf_sentiment$negative[ order(tf_sentiment$negative$prob_lift, decreasing = TRUE) , ], 10)

# what about bi-grams?
tf_sentiment_bigram <- lapply(tf_sentiment, function(x){
  x <- x[ stringr::str_detect(x$term, "_") , ]
  x[ order(x$prob_lift, decreasing = TRUE) , ]
})

head(tf_sentiment_bigram$positive, 10)

head(tf_sentiment_bigram$negative, 10)


```


## Topic modeling

textmineR has extensive functionality for topic modeling. You can fit Latent Dirichlet Allocation (LDA), Correlated Topic Models (CTM), and Latent Semantic Analysis (LSA) from within textmineR. (Examples with LDA and LSA follow below.) As of this writing, textmineR's LDA and CTM functions are wrappers for other packages to facilitate a consistent workflow. Plans exist to impelement LDA natively with `Rcpp` sometime in 2018.

textmineR's consistent representation of topic models boils down to two matrices. The first, "theta" ($\Theta$), has rows representing a distribution of topics over documents. The second, phi ($\Phi$), has rows representing a distribution of words over topics. In the case of probabilistic models, these are categorical probability distributions. In the case of non-probabilistic models (e.g. LSA) these distributions are, obviously, not probabilities. In the case of LSA, for example, there is a third object representing the sigular values in the decomposition.

In addition, textmineR has utility functions for topic models. This includes some original research. Examples include an R-squared for probabilistic topic models ([working paper here](https://drive.google.com/file/d/0Bz2enPyUvnKIQmtDTEswbzdUMU0/view)), probabilistic coherenc (a measure of topic quality), and a topic labeling function based on most-probable bigrams. Other utilities are demonstrated below

### LDA Example
```{r lda_example}

# start with a sample of 500 documents so our example doesn't take too long
dtm_sample <- dtm[ sample(1:nrow(dtm), 500) , ]

# Fit a Latent Dirichlet Allocation model
# note the number of topics is arbitrary here
# see extensions for more info
model <- FitLdaModel(dtm = dtm_sample, 
                     k = 100, 
                     iterations = 800,
                     alpha = 0.1, # this is the default value
                     beta = 0.05) # this is the default value

# two matrices: 
# theta = P(topic | document)
# phi = P(word | topic)
str(model)

# R-squared 
# - only works for probabilistic models like LDA and CTM
model$r2 <- CalcTopicModelR2(dtm = dtm_sample, 
                             phi = model$phi,
                             theta = model$theta)

model$r2

# log Likelihood (does not consider the prior) 
# - only works for probabilistic models like LDA and CTM
model$ll <- CalcLikelihood(dtm = dtm_sample, 
                           phi = model$phi, 
                           theta = model$theta)

model$ll

# probabilistic coherence, a measure of topic quality
# - can be used with any topic model, e.g. LSA
model$coherence <- CalcProbCoherence(phi = model$phi, dtm = dtm_sample, M = 5)

summary(model$coherence)

hist(model$coherence, col= "blue")

# Get the top terms of each topic
model$top_terms <- GetTopTerms(phi = model$phi, M = 5)

head(t(model$top_terms))

# Get the prevalence of each topic
# You can make this discrete by applying a threshold, say 0.05, for
# topics in/out of docuemnts. 
model$prevalence <- colSums(model$theta) / sum(model$theta) * 100

# textmineR has a naive topic labeling tool based on probable bigrams
model$labels <- LabelTopics(assignments = model$theta > 0.05, 
                            dtm = dtm_sample,
                            M = 1)

head(model$labels)

# put them together, with coherence into a summary table
model$summary <- data.frame(topic = rownames(model$phi),
                            label = model$labels,
                            coherence = round(model$coherence, 3),
                            prevalence = round(model$prevalence,3),
                            top_terms = apply(model$top_terms, 2, function(x){
                              paste(x, collapse = ", ")
                            }),
                            stringsAsFactors = FALSE)

View(model$summary[ order(model$summary$prevalence, decreasing = TRUE) , ])

# Get topic predictions for all 2,000 documents

# first get a prediction matrix, phi is P(word | topic)
# we need P(topic | word), or "phi_prime"
model$phi_prime <- CalcPhiPrime(phi = model$phi,
                                theta = model$theta)

# set up the assignments matrix and a simple dot product gives us predictions
assignments <- dtm / rowSums(dtm)

assignments <- assignments %*% t(model$phi_prime)

assignments <- as.matrix(assignments) # convert to regular R dense matrix

# compare the "fit" assignments to the predicted ones
barplot(model$theta[ rownames(dtm_sample)[ 1 ] , ], las = 2,
        main = "Topic Assignments While Fitting LDA")

barplot(assignments[ rownames(dtm_sample)[ 1 ] , ], las = 2,
        main = "Topic Assignments Predicted Under the Model")

```

Depending on your application, you can reformat the outputs of phi, theta, assignments, the summary table etc. to suite your needs. For example, you can build a "semantic" search of your documents by vectorizing the query with `CreateDtm`, then predicting under the model with phi_prime.

As of this writing, you will have to take care to make sure your vocabulary aligns. (I'd suggest using something like `intersect(colnames(dtm), colnames(theta))`.) Part of the big 2018 update will be creating a predict method that will handle this for you.

### LSA Example

Latent semantic analysis was arguably the first topic model. [LSA was patented in 1988](https://en.wikipedia.org/wiki/Latent_semantic_analysis). It uses a single value decomposition on a document term matrix, TF-IDF matrix, or similar. 

The workflow for LSA is largely the same for LDA. Two key differences: we will use the IDF vector mentioned above to create a TF-IDF matrix and we cannot get an R-squared for LSA as it is non-probabilistic. 

```{r lsa_example}

# get a tf-idf matrix
tf_sample <- TermDocFreq(dtm_sample)

tf_sample$idf[ is.infinite(tf_sample$idf) ] <- 0 # fix idf for missing words

tf_idf <- t(dtm_sample / rowSums(dtm_sample)) * tf_sample$idf

tf_idf <- t(tf_idf)

# Fit a Latent Semantic Analysis model
# note the number of topics is arbitrary here
# see extensions for more info
lsa_model <- FitLsaModel(dtm = tf_idf, 
                     k = 100)

# three objects: 
# theta = distribution of topics over documents
# phi = distribution of words over topics
# sv = a vector of singular values created with SVD
str(lsa_model)


# probabilistic coherence, a measure of topic quality
# - can be used with any topic lsa_model, e.g. LSA
lsa_model$coherence <- CalcProbCoherence(phi = lsa_model$phi, dtm = dtm_sample, M = 5)

summary(lsa_model$coherence)

hist(lsa_model$coherence, col= "blue")

# Get the top terms of each topic
lsa_model$top_terms <- GetTopTerms(phi = lsa_model$phi, M = 5)

head(t(lsa_model$top_terms))

# Get the prevalence of each topic
# You can make this discrete by applying a threshold, say 0.05, for
# topics in/out of docuemnts. 
lsa_model$prevalence <- colSums(lsa_model$theta) / sum(lsa_model$theta) * 100

# textmineR has a naive topic labeling tool based on probable bigrams
lsa_model$labels <- LabelTopics(assignments = lsa_model$theta > 0.05, 
                            dtm = dtm_sample,
                            M = 1)

head(lsa_model$labels)

# put them together, with coherence into a summary table
lsa_model$summary <- data.frame(topic = rownames(lsa_model$phi),
                            label = lsa_model$labels,
                            coherence = round(lsa_model$coherence, 3),
                            prevalence = round(lsa_model$prevalence,3),
                            top_terms = apply(lsa_model$top_terms, 2, function(x){
                              paste(x, collapse = ", ")
                            }),
                            stringsAsFactors = FALSE)

View(lsa_model$summary[ order(lsa_model$summary$prevalence, decreasing = TRUE) , ])

# Get topic predictions for all 2,000 documents

# first get a prediction matrix,
lsa_model$phi_prime <- diag(lsa_model$sv) %*% lsa_model$phi

lsa_model$phi_prime <- t(MASS::ginv(lsa_model$phi_prime))

# set up the assignments matrix and a simple dot product gives us predictions
lsa_assignments <- t(dtm) * tf_sample$idf

lsa_assignments <- t(lsa_assignments)

lsa_assignments <- lsa_assignments %*% t(lsa_model$phi)

lsa_assignments <- as.matrix(lsa_assignments) # convert to regular R dense matrix

# compare the "fit" lsa_assignments to the predicted ones
# distribution is the same, but scale changes
barplot(lsa_model$theta[ rownames(dtm_sample)[ 1 ] , ], las = 2,
        main = "Topic Assignments While Fitting LSA")

barplot(lsa_assignments[ rownames(dtm_sample)[ 1 ] , ], las = 2,
        main = "Topic Assignments Predicted Under the Model")

```


### Extensions

#### Document clustering is just a special topic model
Document clustering can be thought of as a topic model where each document contains exactly one topic. textmineR's `Cluster2TopicModel` function allows you to take a clustering solution and a document term matrix and turn it into a probabilistic topic model representation. You can use many of textmineR's topic model utilities to evaluate your clusters (e.g. R-squared, coherence, labels, etc.)

#### Choosing the number of topics
There is no commonly accepted way to choose the number of topics in a topic model. Fear not! Probabilistic coherence can help you. In forthcoming research, I show that probabilistic coherence can find the correct number of topics on a simulated corpus where the number of topics is known beforehand. (This will be part of a PhD dissertation, sometime around 2021. Stand by!)

Users can implement this procedure. Simply fit several topic models across a range of topics. Then calculate the probabilistic coherence for each topic in each model. Finally, average the probabilistic coherence across all topics in a model. This is similar to using the [silhouette coefficient](https://en.wikipedia.org/wiki/Silhouette_(clustering)) to select the number of clusters when clustering.

Some example code (on a trivially small dataset) is below.

```{r select_number_topics}
# load a sample DTM
data(nih_sample_dtm)

# choose a range of k 
# - here, the range runs into the corpus size. Not recommended for large corpora!
k_list <- seq(5, 95, by = 5)

# set up a temporary directory to store fit models so you get partial results
# if the process fails or times out. This is a trivial example, but with a decent
# sized corpus, the procedure can take hours or days, depending on the size of 
# the data and complexity of the model.
# I'm using the digest function to create a hash so that it's obvious this is a 
# temporary directory
model_dir <- paste0("models_", digest::digest(colnames(nih_sample_dtm), algo = "sha1"))

if (!dir.exists(model_dir)) dir.create(model_dir)

# Fit a bunch of LDA models
# even on this trivial corpus, it will a bit of time to fit all of these models
model_list <- TmParallelApply(X = k_list, FUN = function(k){
  filename = file.path(model_dir, paste0(k, "_topics.rda"))

  if (!file.exists(filename)) {
    m <- FitLdaModel(dtm = nih_sample_dtm, k = k, iterations = 500)
    m$k <- k
    m$coherence <- CalcProbCoherence(phi = m$phi, dtm = nih_sample_dtm, M = 5)
    save(m, file = filename)
  } else {
    load(filename)
  }
  
  m
}, export=c("nih_sample_dtm", "model_dir")) # export only needed for Windows machines

# Get average coherence for each model
coherence_mat <- data.frame(k = sapply(model_list, function(x) nrow(x$phi)), 
                            coherence = sapply(model_list, function(x) mean(x$coherence)), 
                            stringsAsFactors = FALSE)


# Plot the result
# On larger (~1,000 or greater documents) corpora, you will usually get a clear peak
plot(coherence_mat, type = "o")
    

```


#### Other topic models
Topic models from other packages can be used with textmineR. The workflow would look something like this:

1. Use `CreateDtm` to create a curated DTM
2. Use `Dtm2Docs` to re-create a text vector of curated tokens from your DTM
3. Fit a topic model using your desired package (for example, [mallet](https://cran.r-project.org/web/packages/mallet/index.html))
4. Format the raw output to have two matrices, phi and theta as above
5. Use textmineR's suite of utility functions with your model

## Text embeddings 
Text embeddings are particularly hot right now. While textmineR doesn't (yet) explicitly implement any embedding models like GloVe or word2vec, you can still get embeddings. Text embedding algorithms aren't conceptually different from topic models. They are, however, operating on a different matrix. Instead of reducing the dimensions of a document term matrix, text embeddings are obtained by reducing the dimensions of a term co-occurrence matrix. In principle, one can use LDA or LSA in the same way. In this case, rows of theta are embedded words. A phi_prime may be obtained to project documents or new text into the embedding space.

What follows is a quick example of this using LDA as the embedding mechanism.

```{r embedding}

# First create a TCM using skip grams, we'll use a 5-word window
# most options available on CreateDtm are also available for CreateTcm
tcm <- CreateTcm(doc_vec = movie_review$review,
                 skipgram_window = 5)

# use LDA to get embeddings into probability space
# This will take considerably longer as the TCM matrix has many more rows 
# than a DTM
embeddings <- FitLdaModel(dtm = tcm,
                          k = 100,
                          iterations = 800)

# Get an R-squared for general goodness of fit
embeddings$r2 <- CalcTopicModelR2(dtm = tcm, 
                                  phi = embeddings$phi,
                                  theta = embeddings$theta)

embeddings$r2

# Get coherence (relative to the TCM) for goodness of fit
embeddings$coherence <- CalcProbCoherence(phi = embeddings$phi,
                                          dtm = tcm)

summary(embeddings$coherence)

# Get top terms, no labels because we don't have bigrams
embeddings$top_terms <- GetTopTerms(phi = embeddings$phi,
                                    M = 5)

head(t(embeddings$top_terms))

# Create a summary table, similar to the above
embeddings$summary <- data.frame(topic = rownames(embeddings$phi),
                                 coherence = round(embeddings$coherence, 3),
                                 prevalence = colSums(embeddings$theta) / 
                                   sum(embeddings$theta) * 100,
                                 top_terms = apply(embeddings$top_terms, 2, function(x){
                                   paste(x, collapse = ", ")
                                 }),
                                 stringsAsFactors = FALSE)

View(embeddings$summary[ order(embeddings$summary$prevalence, decreasing = TRUE) , ])

# Embed the documents
dtm_embed <- CreateDtm(doc_vec = movie_review$review,
                       doc_names = movie_review$id,
                       ngram_window = c(1,1))

dtm_embed <- dtm_embed[ , colnames(tcm) ] # make sure vocab lines up

embeddings$phi_prime <- CalcPhiPrime(phi = embeddings$phi,
                                     theta = embeddings$theta)

embedding_assignments <- dtm_embed / rowSums(dtm_embed)

embedding_assignments <- embedding_assignments %*% t(embeddings$phi_prime)

embedding_assignments <- as.matrix(embedding_assignments)

# get a goodness of fit relative to the DTM
embeddings$r2_dtm <- CalcTopicModelR2(dtm = dtm_embed, 
                                      phi = embeddings$phi,
                                      theta = embedding_assignments)

embeddings$r2_dtm

# get coherence relative to DTM
embeddings$coherence_dtm <- CalcProbCoherence(phi = embeddings$phi,
                                              dtm = dtm_embed)

summary(embeddings$coherence_dtm)

```

You could just as easily use LSA as your embedding, or any other dimensionality reduction/matrix factorization method. The advantge of using the `dgCMatrix` is that it is so widely supported in the R ecosystem.

Embeddings are only recently being researched. However, they may be used in very similar contexts to topic models. It's just that the "topics" are fit another way.

## Building a basic document summarizer
Let's use the above embeddings model to create a document summarizer. This will return the three most relevant sentences in each review.

```{r summaries}

library(igraph) 

# let's do this in a function

summarizer <- function(doc, phi_prime) {
  
  # recursive fanciness to handle multiple docs at once
  if (length(doc) > 1 )
    return(sapply(doc, function(d) summarizer(d, phi_prime)))
  
  # parse it into sentences
  sent <- stringi::stri_split_boundaries(doc, type = "sentence")[[ 1 ]]
  
  names(sent) <- seq_along(sent) # so we know index and order
  
  # embed the sentences in the model
  e <- CreateDtm(sent, ngram_window = c(1,1), verbose = FALSE)
  
  vocab <- intersect(colnames(e), colnames(phi_prime))
  
  e <- e / rowSums(e)
  
  e <- e[ , vocab ] %*% t(phi_prime[ , vocab ])
  
  e <- as.matrix(e)
  
  # get the pairwise distances between each embedded sentence
  e_dist <- CalcHellingerDist(e)
  
  # turn into a similarity matrix
  g <- 1 - e_dist * 100
  
  diag(g) <- 0
  
  # turn into a nearest-neighbor graph
  g <- apply(g, 1, function(x){
    x[ x < sort(x, decreasing = TRUE)[ 3 ] ] <- 0
    x
  })

  g <- pmax(g, t(g))
  
  g <- graph.adjacency(g, mode = "undirected", weighted = TRUE)
  
  # calculate eigenvector centrality
  ev <- evcent(g)
  
  # format the result
  result <- sent[ names(ev$vector)[ order(ev$vector, decreasing = TRUE)[ 1:3 ] ] ]
  
  result <- result[ order(as.numeric(names(result))) ]
  
  paste(result, collapse = " ")
}

# Let's see the summary of the first couple of reviews
docs <- movie_review$review[ 1:3 ]
names(docs) <- movie_review$id[ 1:3 ]

sums <- summarizer(docs, phi_prime = embeddings$phi_prime)

sums
```
